\section{Discussion}\label{sec:discussion}

The model previously developed arose from the search for the intersection of two
different sets of necessities. On one side, the necessities of holographic physics and
its already-developed framework---quantum tori, strings, holography, information---which
are forced by the physics itself. On the other, the necessities of mathematics: which
paths are open and which are blocked, if the physics is to be described as it requires to
be described. The object both sets must accommodate is the participatory observer with no
exterior, in de~Sitter space.

We approached the intersection in a manner that may be called Barthesian, applied to
these shared mathematical necessities---in this case, the problem of self-reference.
Barthes holds that there is a degree zero of writing: a structure prior to the present
language which precedes it and allows it to signify~\cite{Barthes53}. Here we sought the
analogous structure common to, and prior to, the mathematical and the physical languages
that must intersect. The structure we found is twofold in one. As ancestor and common
point, it is the vanishing point of drawing, industrial design and architecture: the
Vitruvian module---the historical and etymological ancestor of isometry, of the modulus
of $\C$, and of the modular spaces that precede the contemporary moduli spaces and still
underlie them. And as shared fundamental principles between the two sets of necessities,
it is $\pi$, $\golden$, polygons and trigonometry: an entire language, and a way of
approaching moduli spaces. Joined with $\golden$, a practice likewise descending from the
arts, the module parametrises the whole space of a building with a single magnitude and
thereby carries diverse ratios into one space; we use exactly this to bridge arithmetic
and geometry, treating arithmetic as ratios, polygons and trigonometry, and from that
prior structure the framework is built within a string---parametrising a worldsheet.

The discussion follows one route. \S\ref{ssec:disc-problem} sets out the problem in fuller form than the introduction: existing theories leave no place for the observer. \S\ref{ssec:disc-proposal} states our proposal as a theory, recasting the self-reference so that it is no longer a paradox. \S\ref{ssec:disc-resolution} gives the solution---the geometric mediation $\pi/\golden$, and the mathematical detail of its execution, where it meets Manin's ideas on the same object (developed in \S\ref{sec:methods}). \S\ref{ssec:disc-string} shows the string and torus this produces, and how that mathematical structure connects to holography and M-theory through its AdS/CFT link (developed in \S\ref{sec:derivations}). \S\ref{ssec:disc-yields} gathers what follows from it in de~Sitter (developed in \S\ref{sec:implications}), where the framework meets relativity and the quantum along Witten's criteria on the von~Neumann types. \S\ref{ssec:disc-closure} closes by returning to the self-reference and the epistemological limit the paper began with.

\subsection{The problem: an observer with no place}\label{ssec:disc-problem}

\emph{M-theory from the Superpoint}~\cite{huerta2018m,Huerta2019emerge} showed that the spacetimes of string theory and M-theory are not postulates but consequences. Starting from the superpoint $\R^{0|1}$---an object with a trivial (abelian) Lie bracket, no metric, and no spin structure---and iterating maximal invariant central extensions classified by super-Lie-algebra cohomology, one recovers super-Minkowski spacetime in dimensions $3,4,6,10$, and $11$, and from these the entire brane content~\cite{FiorenzaSatiSchreiber15}. The Lorentz metric is never put in by hand; it appears in the automorphisms of the algebra. The result is remarkable, but it is written wholly in the third person. There is no observer anywhere in it. The metric appears---but to whom? The construction is a ladder, played as a game of two moves from outside the system, and it never asks where an observer would stand. In Minkowski or anti--de~Sitter space that silence is harmless. In de~Sitter space, which has no reachable spatial boundary and no outside, it is not: a de~Sitter universe is closed upon itself, and whatever observes it must be inside it.

Our program takes that omission as its problem. The question is how to place the observer inside de~Sitter space, where there is no exterior to retreat to. We share the superpoint's philosophical root---Hegel's opening, in which Being and Nothing are identical and their truth is Becoming---but we realize it in a form that has room for an observer, using $\golden$ and $\pi$.

The Hegelian content of the construction enters through Lawvere's categorical formalization of Hegel's \emph{Science of Logic}. Lawvere formalizes the \emph{unity and identity of opposites} as an adjunction, with adjoint functors as the basic instance~\cite{lawvere96unity}; under the resulting dictionary, \emph{pure being} and \emph{nothing} are the terminal and initial objects---the right and left adjoints of $(\varnothing \dashv \ast)$---\emph{becoming} is an adjoint modality, and \emph{determinate being} (Dasein) is the \emph{Aufhebung} of $(\varnothing \dashv \ast)$, realized as the next higher level in the lattice of essential subtoposes. Cohesion is axiomatized as an adjoint quadruple $(\Pi_0 \dashv \mathrm{Disc} \dashv \Gamma \dashv \mathrm{coDisc})$~\cite{Schreiber13cohesive}, and the superpoint $\R^{0|1}$ is an object of the corresponding \emph{super cohesion}---Schreiber's \emph{solid cohesion}, the $\infty$-topos of super formal smooth $\infty$-groupoids, cohesive over the base topos of bare super-sets~\cite{Schreiber13cohesive}. From it, super-Minkowski spacetime and the brane bouquet are obtained by consecutive \emph{maximal invariant central extensions}, classified at each stage by the invariant even super Lie algebra cohomology; the three-dimensional super-Minkowski algebra, for instance, is the maximal invariant central extension of the superpoint $\R^{0|2}$, induced by the symmetric bilinear forms that span its even second cohomology~\cite{huerta2018m}.

This realizes the \emph{form} of the unity of opposites---the adjunction---but between \emph{distinct} objects: the initial and terminal objects are not identified. The construction is correspondingly one-directional: the brane bouquet is rooted in the superpoint and grows outward by consecutive central extensions---$0$-brane condensation from nothing---never closing back upon its origin. So realized, the dialectical becoming carries neither an observer nor a selected vacuum. The opposite difficulty is met in low-dimensional holography, in the \emph{ensemble problem}: where M-theory leaves the observer outside, AdS/CFT depends on the observer but cannot put it inside---no single boundary theory is available, and the bulk survives only as an average over an \emph{ensemble} of them, even though quantum gravity should carry discrete, individual microstates of its own~\cite{Cooper2026}.

\subsection{Our theoretical proposal}\label{ssec:disc-proposal}

Hegel's becoming was realized above through Lawvere, as the unity of opposites between distinct objects. We realize it from a different perspective---one that draws from Oberarzbacher, analysing Hegel through the non-dualist perspective of the Shaivism of Kashmir~\cite{Oberarzbacher2013}. For Hegel the absolute is reached by contrasting opposites: the unity is won as their \emph{conciliation}, and the principle of non-contradiction is the engine that drives the opposition. In Shaivism it is otherwise: the unity is not a synthesis of opposites but is given first---the Self unfolds as Subject and Object already in a correlation of identity, and what is reached is the \emph{recognition} of that identity, not its production; there the principle of non-contradiction is not the engine but the faculty that fabricates the duality of Subject against Object.

We take the non-dual route and render it mathematically through functors, as in the case of Lawvere's but with a twist; geometrically, ratios as terms classified as equivalent. We do so on the base of the Vitruvian rhetoric, read with Foucault and Barthes as the degree zero of the geometrical episteme~\cite{Foucault66,Barthes53}: the pre-Cartesian mode of interpretation in which things are related not by binary Cartesian logic but by adjustments, ligaments and junctures---through number, proportion and the anatomy of the things compared~\cite{Santos2020}. On that base we classify the circle of $\C$ and the wave function as Euler's identity, under their geometric equivalences as circles, and as lines in relation to the integers, the reals and the primes through $\golden$. $\golden$, in turn, lets us relate this construction to the appearance of $\golden$ in the wave functions of physics, rather than in number theory.

In simple terms, to create intuition for the framework developed in \S\ref{sec:methods}: we take $\golden$, which we find as a function and an operator, as well as a ratio, in different areas of wave functions and lattices~\cite{Pletser2018,Jagannathan2021,Jedrkiewicz2018,Sonnino2024}. And that $\golden$ we carry across the whole plane through an algebraic ring (the string) working as a Vitruvian module, which has been used for millennia in art to carry one and the same magnitude over the plane and also onto a three-dimensional object. The Vitruvian module is the common measure taken from the column at its base, from whose single magnitude the \emph{symmetriae} and proportions of the whole building are derived by \emph{commodulatio} (Vitruvius, \emph{De arch.}~3.1.1): every part stands in fixed ratio to the module and, through it, to the central axis, conferring unity and proportion on the whole as the disposition of parts does in rhetoric~\cite{Santos2020}. It was the basis of Brunelleschi's and Alberti's perspective, and it is in fact the ancestor of the module of $\C$ and of the isometric lattice as well. In abstract mathematical terms its components are: an origin, a radius, a magnitude, an angle, six-fold hexagonal symmetry, trigonometry and polygons---in this case, to distribute $\golden$ across the plane and across dimensions and space in a completely self-consistent way.

Finally, this module/ring is mounted on the noncommutative torus that M-theory uses, its non-orientable fibre---independent of the algebra (Proposition~\ref{prop:mobius-torus})---taking it from interior to exterior with $\tfrac12$, a topological relation that makes it similar to an AdS/CFT throat.

The result lets us connect the geometry of $\pi$ in the quantum paths taken with equivalence of value: $\pi$ weighs every path with equal importance, so that none is privileged. But here fixed by the cutoff $\varepsilon_0$ with $\varepsilon_0\Mpcf=\pi$, and tied to the string as an accumulation of information, which is likewise non-privileged.

Thus $\pi$ and $\golden$ become, at the same time, the point of contact between the wave function, the string as a Vitruvian module, and $\C$. What the Vitruvian module achieves in $\C$ is, through its properties ($\pi$, $\golden$, polygons and trigonometry), to generate a relation to the Euler product and the values of $\zeta$, as well as to the primes---this is demonstrated in full in other papers~\cite{Corr,F1}. What it allows here, independently of the primes, because we are in physics, is to unite the geometry of $1$D with the $2$D structure of $\C$ and with the $3$D isometric, self-consistently.

We could then say that it is a bridge between a new kind of space and a very old one---a steampunk kind of space: a contemporary, neoclassical/Victorian, idealized reconstruction of the ancients that employs the principles preceding the module space of $\C$ and the isometric space, which are relevant in the Vitruvian module, placing them within the territory of string theory through the contact of $\pi$ and $\golden$.

\subsection{The resolution: geometric mediation---\texorpdfstring{$\pi/\golden$}{pi/phi}}\label{ssec:disc-resolution}

The relation the module opens in $\C$---to the Euler product, $\zeta$ and the primes, on one side, and, on the other, to the very places where $\zeta$ already appears in physics: the odd zeta values $\zeta(2k+1)$ fixed by the Veneziano string amplitude~\cite{Elvang2026,Veneziano}.

This intersection yields something similar to Manin's hypothesis for tackling the Riemann hypothesis: the tori that M-theory uses, carried to the $\F_1$ program, with Borger's $\Lambda$-ring of Frobenius lifts fixing their arithmetic~\cite{manin04,F1}. Here, though, the same object is turned to holography in place of $\F_1$, in the M-theory noncommutative tori. The mediation works through three mediators, and closes, below, on the very Frobenius lifts, the Artin character $\chi_5$ and the Euler product it reaches.

The $\F_1$ program is, in essence, a geometric descent meant to avoid circularity. Beyond its link to strings, the same program has been connected to the Hermitian-operator problem---the Hilbert--P\'olya route: a self-adjoint operator whose spectrum would carry the zeros without reference to the $\zeta$ values or the primes, pursued in the modern era by Berry and Keating, by Bender, Brody and M\"uller, and from noncommutative geometry by Connes (see the companion paper~\cite{HP} for the full lineage). This is significant for the present theme, because that program seeks to recreate the spectrum of the zeros of $\zeta$ without the exact GUE statistical ensemble that low-dimensional AdS/CFT falls back on; our proposal for that operator is constructed in the same companion paper~\cite{HP}. What we do here is to try to join the necessities of holography with M-theory: in the spirit of Maldacena's ideas about the use of M-theory's tori for holography, and of our reinterpretation of the superpoint, turning a similar object to the holographic problem rather than to $\F_1$.

The three mediators join $0$ and $1$: the \textbf{half}, $\pi$, and $\golden$. Each mediator carries a definite function. The \textbf{half} is the midpoint between $0$ and $1$: it is the value the diagonal lacked, now present as the contraction norm $\|\widehat\Om\|=\tfrac12$ and as the reference point $\Gamma(\tfrac12)$ between unity and infinity. On the side of $\C$, $\pi$ enters through the half-factorial $\Gamma(\tfrac12)=\sqrt\pi$, whose role is to seat the Gaussian and the factorials of quantum theory and string theory on the circle itself; the circle, carrying the half, meets $i$---the Gaussian lattice and the modulus of $\C$. On the side of the Vitruvian module, $\golden$ enters through the pentagon (its function is to fix the self-similar ratio, $\golden^2=\golden+1$), the triangle enters again through the half (the $\sqrt3/2$, the role of which is to set the ternary norm), and the Mersenne numbers and the powers of $\golden$ enter through $\golden$ and the $3/2$ ratio (their function is to lock $\golden$ to the integers, $3\cdot\golden^{\sigma(p)}=2^p$). On the quantum side the same $\pi$ returns in Euler's identity, bound there to $i$, $e$, and to $1$ and $0$ themselves~\cite{Corr}, where its role is to close the complex rotor on the same $0$ and $1$ the half mediates.

What ties these together are exact bridges, each a specific identity rather than an analogy: \textbf{between $10$ and $1$}---the decagon and the unit: $\zeta_{10}$ the primitive tenth root of unity, $\golden=\zeta_{10}+\zeta_{10}^{-1}$, with $\Q(\golden)\subset\Q(\zeta_{10})\subset\Q(\zeta_{20})$ ($\zeta_{10}=\zeta_{20}^2$, $20=2\cdot10$), and the $1$ of $e^{i\pi}+1=0$, in the multiplicative mediation that scales from $1$ up to the next integer base $2$~\cite{Corr}; \textbf{between $5$ and $10$}---the pentagon and the decagon, $\golden=2\cos(\pi/5)=\zeta_{10}+\zeta_{10}^{-1}$, placing $\golden$ in the real subfield of $\Q(\zeta_{20})$~\cite{Corr}; \textbf{between $\pi$ and $\golden$}---the same trigonometric identity $\golden=2\cos(\pi/5)$, in which the angle $\pi/5$ binds $\pi$ to $\golden$ on the real line~\cite{Corr}; \textbf{between $\golden$ and the integers}---the universal identity $3\cdot\golden^{\sigma(p)}=2^p$, with $\sigma(p)=p\lng-\log_\golden 3$ and the factor $3=M_2=2^2-1$, the first Mersenne prime~\cite{Corr,F1}; and \textbf{between $\pi$ and the integers}---the even zeta values $\zeta(2k)\in\Q\cdot\pi^{2k}$ (Basel for $k=1$), together with the mode count $\lfloor\pi\golden^\sigma\rfloor$ on the tower~\cite{F1}. These do not so much \emph{impose} equivalences across the different domains as \textbf{reveal} that the equivalences were already exact and simultaneous---in the precise sense that one and the same $\golden$ satisfies all of them at once: the twelve clauses across five canonical structures (the complex rotor of Euler's identity, the real trigonometric line, the real-multiplicative line, the Mersenne arithmetic modulo $20$, and the Galois group of $\Q(\zeta_{20})/\Q$) hold under a single $\golden$, with no ordering among them, so the equivalences are \emph{co-constituted}, not matched one after another~\cite{Corr}.

This is what lets us go beyond Lawvere's two-term unity and make all three Hegelian moments coincide: \textbf{Nothing, Being, and Becoming as one}---not in sequence but at one stroke. The static isomorphism of $0$ and $1$ is the circle; the becoming is the dynamics; and the becoming is co-equal with the other two because it is anchored, in the same single $\golden$, in arithmetic---the becoming is not first the circle and then its dynamics, but the one $\golden$ read at once as static identity and as motion. The anchoring recovers the structure of the primes (the Frobenius lifts, the Artin character $\chi_5$, the Euler product)~\cite{F1} and the zeros of $\zeta$, which appear in the vacuum amplitudes themselves, where the partition function is a gas of oscillators labelled by the primes~\cite{Julia90,DeClerckHartnollYang25}.

\subsection{String reconfiguration: the resulting torus and its AdS/CFT connection}\label{ssec:disc-string}

The string of \S\ref{ssec:disc-proposal} closes, geometrically, into a torus. Its worldline $\Om(\tau)=\tfrac12\,e^{\,i\tau\ln\golden}$ (modulus $|\Om|=\tfrac12$), promoted to a worldsheet by the Polyakov action, closes on the torus generated by $\golden$ (\S\ref{ssec:construction},~\eqref{eq:torus}), along whose throat the radial coordinate is $z(\sigma)=\golden^\sigma$. The relation the torus carries is AdS/CFT, but realized without a privileged side: bulk and boundary are joined by an isometry $V:\mathcal H_{\mathrm{bulk}}\to\mathcal H_\partial$ with $V^\dagger V=1$~\cite{HP}, so where orthodox holography integrates out the radial coordinate and keeps only the boundary, here neither side is singled out and both are kept. The modulus is scale-invariant---$|\Om|_\sigma=\tfrac12$ for every $\sigma$---so the relation holds at each level of the throat, not only at the boundary.

This bulk--boundary map is the physical counterpart of the Frobenius lifts already at work in the arithmetic (\S\ref{ssec:disc-resolution})~\cite{F1}. There the lift $\psi_p(\golden^n)=\golden^{pn}$ is computed \emph{as an algebra}---a ring endomorphism of the golden monoid, for every prime $p$ and every $n$. Here it cannot be: there is no three-dimensional division algebra to carry the isometry directly, since a complex space of complex dimension $n$ is a real space of dimension $2n$---so ``complex dimension three'' is $\R^6$, never $\R^3$, and $\R^3$ is odd, with no complex structure. The relation between bulk and boundary must therefore be \emph{recoded between algebra and geometry} rather than computed as an algebra~\cite{HP}---that is the twist. The recoding is geometric of necessity, not by choice: under the Tarskian descent to the real closed fields, which already contain Euclidean geometry~\cite{tarski52}, nothing can be assigned a code at all.

What holds the recoding together at every level is the same half that \S\ref{ssec:disc-resolution} identified as the contraction's fixed point: $|\Om|_\sigma=\tfrac12$ for all $\sigma$ is the physical analogue of $\psi_p(\golden^n)=\golden^{pn}$ for all $p$ and $n$---one $\golden$-tower, read on its physical side. That half-turn is the anti-diagonal in geometric form: a full turn would implement the self-application $f(f)$ that Lawvere prohibits~\cite{lawvere69}, while the half-turn is the distributed passage $f\circ g\circ h$ that does not close. And it is the scale-invariant $|\Om|_\sigma=\tfrac12$ for all $\sigma$---the physical analogue of $\psi_p(\golden^n)=\golden^{pn}$ for all $p$ and $n$.

The same torus carries the rest of the M-theory duality web, and each duality is here a symmetry of the golden tower rather than a separate postulate. S-duality, $\tau\to-1/\tau$, is the Galois conjugation $\golden\to-1/\golden=\bar\golden$ of the golden field: the two arithmetic conjugates of $\golden$ are the strong and weak coupling of the string. T-duality, $R\to\alpha'/R$, is carried by the self-dual radius $R^{2}=\alpha'$ of the same torus, the point the tower fixes\,\Lean{Tdual\_selfdual}. The strong-coupling limit of type~IIA, $\sigma=10\to11$, is the one further step of the tower into eleven dimensions---the passage to M-theory read as one more level. And the de~Sitter swampland condition $|\partial_\sigma V|/V=\ln\golden$~\cite{Obied18} is met by the tower itself, its logarithmic growth rate being exactly $\ln\golden$: the condition an accelerating universe must satisfy is the growth law of the construction. The web is thus not imported; it is what the modulus-preserving symmetries of the $\golden$-tower already are, and its de~Sitter corner is the bridge to the next section.

\subsection{What the resolution yields}\label{ssec:disc-yields}

\subsubsection{Vacuum selection}\label{sssec:disc-vacuum}

The vacuum selection is the second face of the one mechanism, and it bears on relativity because it is the same field read twice. The microstate is a single definite eigenstate, not the statistical mixture of boundary theories that low-dimensional holography otherwise needs, where the bulk survives only as an average over an ensemble (\S\ref{sssec:ensemble}). No such average is needed here, and the reason is geometric: the horizon of the projection $\Pi$ does not factorise into interior${}\otimes{}$exterior---the type~III signature of a non-local field with no edge at which to separate one region from another (\S\ref{ssec:hinge}, Proposition~\ref{prop:obs-nofirewall}). A field that does not factorise has no ensemble of parts to average over; its state is one---the \textbf{vacuum selection} the superpoint's open ladder could not make.

That same non-factorising type~III field is the curved spacetime of relativity. It opens \S\ref{sec:implications} as the worldsheet and closes it as the de~Sitter metric: the wedge without normal trace and the spacetime are one face, read at two scales. So the single microstate is not a statistical fact prior to the geometry---it \emph{is} the geometry, read as a state. This is why the vacuum selection bears on relativity and not only on holography: the field the observer builds from within, rather than averages over, is the one metric relativity leaves undetermined for an observer inside it (\S\ref{sssec:disc-observer}). Measured against Witten's criteria in \S\ref{sec:implications}, it is the maximally mixed vacuum CLPW require, and because it is one state and not an ensemble, the firewall ambiguity that needs an ensemble average does not arise. The operator that realises this microstate as a self-adjoint operator is built in the companion paper~\cite{HP}.

\subsubsection{The self-modeling observer and gravity}\label{sssec:disc-observer}

The observer is, accordingly, modeled as a one-dimensional object---a worldline that loops and raises its memory up the tower $S(\sigma)=\pi\golden^\sigma$, emerging as a self-similar fractal through $\golden$ and the symmetries, and becoming by observing its own magnitude. The self it becomes-with-respect-to is threefold---the entity, the observing, and what has been observed as self-similar information (the accumulated interior, \S\ref{ssec:disc-string}); its own magnitude is that accumulated information. It is the half-projection: $\|P\|\,\|C\|\,\|F\|=\tfrac12=\|\widehat\Om\|$ (Proposition~\ref{prop:pcf-norms}). Observation does not select among pre-existing geometries---it builds the geometry---and the accumulation of bits drives the gravitational sector by an explicit chain: each observed bit deposits information; the deposited bits accumulate as the entropy $S(\sigma)$ along the tower; that entropy obeys the area law, the Bekenstein--Hawking $\SBH=A/4\GN$~\cite{Bekenstein73,Hawking75}; and the area law, imposed as an equation of state $\delta Q=T\,\delta S$ across local horizons, is exactly Jacobson's derivation of the Einstein equation (\S\ref{ssec:accum})~\cite{Jacobson1995}---with a $\pi$-bit capacity per cell setting the Landauer cost~\eqref{eq:certainty}~\cite{Landauer61}. This is the third register of the one mechanism, the algebraic: the self-reference is non-paradoxical because the structure is ternary, and the No-Diagonal (\S\ref{ssec:arity}) together with the fixed point $\golden^2=\golden+1$---and these are one construction, not one equation. The value the binary diagonal lacked is the fixed point of $x\mapsto 1-x$, namely $\tfrac12$, supplied as the half and as $\|\widehat\Om\|=\tfrac12<1$; $\golden$ is the fixed point of the distinct map $x\mapsto 1+1/x$, i.e.\ $\golden^2=\golden+1$; and the two are tied exactly by $\golden^{-\lambda}=\tfrac12$ ($\golden^{\lambda}=2$---the same $2$ that is the binary base). So $\tfrac12$, $\|\widehat\Om\|=\tfrac12$ and $\golden^2=\golden+1$ coexist in one construction. So an operator that must contain its own spectrum~\cite{HP} is defined without contradiction. The contrast with relativity is exact: relativity gives an absolute block together with the relative, but neither a metric for the observer nor a quantization of what observation is or how it occurs; PCF supplies precisely that, as self-consistency relations.

$\pi$, which asks that all directions be weighed with equal importance, and $\golden$, the self-similarity that we find both in nature and in the primes~\cite{F1}, together yield what the superpoint left empty: an observer that models and describes itself---the wave function measuring itself, the One recognizing itself, connected through every available path by the single act of observation, inside a de~Sitter space with no outside and no paradox.

The Einstein equation this yields is not the anti--de~Sitter one it began from. The passage to de~Sitter is a Wick rotation internal to the eigenvalue geometry itself---not imposed from outside, but the rotation already carried by the three-eigenvalue metric---and it is what turns the AdS throat into the de~Sitter space of the observer. With it the cosmological constant is not an input: fixed by the scale $\ell=1$ and the dimension $d=4$, it takes the value $\Lambda_5=-d(d-1)/2\ell^{2}=-6$, which is exactly the qualitative content of Witten's requirement that the theory ``determine the value of the cosmological constant''~\cite{Witten01dS}. What is fixed here is $\Lambda_5=-6$ in these units, structurally and with no free parameter; the observed ${\sim}10^{-122}$ is a separate matter of scale translation, not derived here. And the matter that sources it is the accumulated entropy itself (Proposition~\ref{prop:obs-matter}): the same tower whose bits built the geometry is, saturated, the matter content---so the observer's information, the geometry, and the matter are one.

\subsubsection{Non-local reality before observation}\label{sssec:disc-nonlocal}

PCF is not Leggett's non-local realism, and for that reason it is not refuted by the experiment of Gr\"oblacher and Zeilinger. The difference lies in \emph{what} is real before observation. Leggett's models predetermine the \textbf{parts}: a hidden variable $\lambda$ fixes the state of the subsystems before measurement---a realism of the parts---even while correlating them non-locally, and that is what experiment rules out~\cite{Leggett03,Groblacher07}. PCF, by contrast, makes the non-local \textbf{whole} real, not the parts. Before observation there are no subsystems carrying values (\S\ref{ssec:noselect}, Proposition~\ref{prop:no-parts}); what is real is the indivisible One---the block, the non-local wave function, the circle that distributes magnitude across all of $\C$. The local---the parts---is not predetermined; it is constituted by self-measurement.

This is the needle PCF threads. Bell rules out predetermined \emph{local} properties~\cite{Bell64}---a prediction confirmed by the Bell-test experiments of Clauser, Aspect, and Zeilinger, the work recognized by the 2022 Nobel Prize in Physics~\cite{FreedmanClauser72,Aspect82,Weihs98,Nobel2022}; Leggett rules out predetermined \emph{subsystem} properties, local or not~\cite{Leggett03}, as the experiment of Gr\"oblacher et al.\ and, independently, that of Branciard et al.\ have shown~\cite{Groblacher07,Branciard07}; PCF denies that there are subsystems at all before observation---only the non-local whole. It is not a realism of the parts but a reality of the whole. This is why ``if it is not observed, it is not there'' refers to the local---the parts, the geometry---and not to the non-local whole, which is real.

The geometric realization is the one built above. $\pi$ weighs all directions with equal importance, so no localization is privileged before observation: that is the non-locality, by construction. The wave function---the phase, the $1$---is the non-local real, not a merely predictive device (the Copenhagen reading we reject); the observer is the wave function itself. Self-measurement constitutes the local: observing builds the geometry rather than selecting among pre-given ones; the non-local measures itself, and the local emerges from it. And $\mathrm{ER}=\mathrm{EPR}$ makes the non-local correlation---entanglement---into geometry itself~\cite{MaldacenaSusskind13} (\S\ref{ssec:accum}, Proposition~\ref{prop:er-epr}): the non-locality before observation is that entangled structure, which observation weaves into geometry.

Why de~Sitter forces this closes the argument. In de~Sitter there is no outside, hence no external frame against which to localize anything. The reality before observation must therefore be the self-contained non-local whole---there can be no pre-given local parts, because there is no exterior to define them---and the only way for anything local to appear is for that whole to measure itself. Non-locality before observation is not an addition; it is forced by the absence of an outside. The non-locally real (the whole, the One) together with the observer-dependence of the local (constituted by self-measurement) is precisely a reality that is \emph{non-locally real and observer-dependent}---evading at once Bell (there is no local realism) and Leggett (there is no realism of the parts).

\subsection{Closure: the self-portrait}\label{ssec:disc-closure}

The same Vitruvian module that Vel\'azquez used to construct the perspective of the interior architecture in \emph{Las Meninas}---where he portrays himself painting himself, at once the painter and the observer of the work~\cite{Foucault66}---is also the one that allowed us to portray the observer, the act of observing, and the observed as one and the same. The divine proportion of that module is the one set out by Pacioli and illustrated by Leonardo~\cite{pacioli1509}. Foucault opens \emph{The Order of Things} with this same canvas, reading it as the limit of the classical \emph{episteme}: the order in which things were known through representation, resemblance and proportion---the order to which the Vitruvian module belongs. This is where the introduction began. There the de~Sitter difficulty was posed as epistemological rather than ontological (\S\ref{sssec:mathrep})---a question of how to represent something self-referential.

The picture is not laid down at once; it is built up cumulatively by observing. Each cycle deposits bits, a cell fills and overflows, the tower $S(\sigma)=\pi\golden^\sigma$ rises, and at the threshold $\tfrac12$ redundant encoding makes each level objective, so that independent observers agree. This is consonant with Kiely's metrological quantum Darwinism~\cite{Kiely26}, with gravity read off from entropy~\cite{Jacobson1995} and from information~\cite{Verlinde2011,Verlinde2017}, with the invariants of Cooper's \emph{Holographic Equidistribution}~\cite{Cooper2026}, and with non-local reality before observation. Just as Vel\'azquez in \emph{Las Meninas}, in this theory the quantum vacuum paints itself a portrait of its true self, painting itself---only its tools are mathematics and physics rather than oil paint.

