\section{Conclusions}\label{sec:conclusions}
The framework establishes two results and joins them into one. First
(\S\ref{sec:methods}--\S\ref{sec:derivations}), a single microstate --- the modulus
$|\Om|=\tfrac12$ --- suffices to derive the AdS/CFT correspondence and, through the
$\golden^{\sigma}$ tower, the M-theory type duality web, with no ensemble average: the correspondence
follows from \emph{one} state, not a statistical family. Second (\S\ref{sec:implications}), this
determinism does not dispense with the observer but recasts its role.

The observer --- the projection $\Pi$ already present in that derivation --- is a genuine
participant, yet not as a \emph{selector} of the vacuum: the microstate is the unique
self-consistent solution, so there is no landscape to choose from. It participates, instead,
through the information that its own act of observing accumulates. That quantum Fisher information
(in Kiely's metrological sense~\cite{Kiely26}) is what builds the geometry --- conjugate to the
tower entropy, bounded by the ultraviolet cuts of \S\ref{sec:derivations}, and, through the
Landauer cost of each bit and the Jacobson--Verlinde passage from entropy to curvature, the source
of the Einstein equations. The observer does not choose the world; it constructs it \emph{without
alternative} --- participatory yet forced. The objectivity threshold $f_{\mathrm{crit}}=\tfrac12$
is reached, and it is the modulus of the microstate: the framework is thereby consonant with Kiely's
quantum Darwinism and, at the same time, with non-local realism.

