\begin{thebibliography}{99}
\bibitem{Strominger01} A.~Strominger, \emph{The dS/CFT correspondence}, JHEP \textbf{10} (2001) 034.
\bibitem{Susskind95} L.~Susskind, \emph{The world as a hologram}, J.~Math.~Phys.\ \textbf{36} (1995) 6377.
\bibitem{Maldacena98} J.~M.~Maldacena, \emph{The large $N$ limit of superconformal field theories and supergravity}, Adv.\ Theor.\ Math.\ Phys.\ \textbf{2} (1998) 231.
\bibitem{SusskindWitten98} L.~Susskind, E.~Witten, \emph{The holographic bound in anti-de Sitter space}, arXiv:hep-th/9805114.
\bibitem{KS00} I.~R.~Klebanov, M.~J.~Strassler, \emph{Supergravity and a confining gauge theory: duality cascades and $\chi$SB-resolution of naked singularities}, JHEP \textbf{08} (2000) 052.
\bibitem{Witten01dS} E.~Witten, \emph{Quantum gravity in de Sitter space}, arXiv:hep-th/0106109.
\bibitem{CLPW22} V.~Chandrasekaran, R.~Longo, G.~Penington, E.~Witten, \emph{An algebra of observables for de Sitter space}, JHEP \textbf{02} (2023) 082.
\bibitem{Susskind03} L.~Susskind, \emph{The anthropic landscape of string theory}, arXiv:hep-th/0302219.
\bibitem{BoussoPolchinski00} R.~Bousso, J.~Polchinski, \emph{Quantization of four-form fluxes and dynamical neutralization of the cosmological constant}, JHEP \textbf{06} (2000) 006, arXiv:hep-th/0004134.
\bibitem{Douglas03} M.~R.~Douglas, \emph{The statistics of string/M theory vacua}, JHEP \textbf{05} (2003) 046, arXiv:hep-th/0303194.
\bibitem{BoussoSusskind11} R.~Bousso, L.~Susskind, \emph{The multiverse interpretation of quantum mechanics}, Phys.\ Rev.\ D \textbf{85} (2012) 045007, arXiv:1105.3796.
\bibitem{SSS19} P.~Saad, S.~H.~Shenker, D.~Stanford, \emph{JT gravity as a matrix integral}, arXiv:1903.11115.
\bibitem{Cooper2026} N.~Cooper, \emph{Holographic equidistribution}, arXiv:2602.12265.
\bibitem{lawvere69} F.~W.~Lawvere, \emph{Diagonal arguments and cartesian closed categories}, Lecture Notes in Math.\ \textbf{92} (1969) 134.
\bibitem{yanofsky03} N.~S.~Yanofsky, \emph{A universal approach to self-referential paradoxes, incompleteness and fixed points}, Bull.\ Symbolic Logic \textbf{9} (2003) 362.
\bibitem{martinlof75} P.~Martin-L\"of, \emph{An intuitionistic theory of types: predicative part}, in \emph{Logic Colloquium '73}, North-Holland (1975).
\bibitem{priest79} G.~Priest, \emph{The logic of paradox}, J.~Philos.\ Logic \textbf{8} (1979) 219.
\bibitem{russell08} B.~Russell, \emph{Mathematical logic as based on the theory of types}, Amer.\ J.\ Math.\ \textbf{30} (1908) 222.
\bibitem{tarski52} A.~Tarski, \emph{A Decision Method for Elementary Algebra and Geometry}, 2nd ed., Univ.\ of California Press (1951).
\bibitem{huerta2018m} J.~Huerta, U.~Schreiber, \emph{M-theory from the superpoint}, Lett.\ Math.\ Phys.\ \textbf{108} (2018) 2695.
\bibitem{Witten95} E.~Witten, \emph{String theory dynamics in various dimensions}, Nucl.\ Phys.\ B \textbf{443} (1995) 85, arXiv:hep-th/9503124.
\bibitem{connes98} A.~Connes, M.~R.~Douglas, A.~Schwarz, \emph{Noncommutative geometry and matrix theory}, JHEP \textbf{02} (1998) 003.
\bibitem{Barthes53} R.~Barthes, \emph{Le Degr\'e z\'ero de l'\'ecriture}, Seuil, Paris (1953).
\bibitem{Hurwitz1891} A.~Hurwitz, \emph{Ueber die angen\"aherte Darstellung der Irrationalzahlen
durch rationale Br\"uche}, Math.\ Ann.\ \textbf{39} (1891) 279.
\bibitem{manin04} Yu.~I.~Manin, \emph{Real multiplication and noncommutative geometry}, in \emph{The Legacy of Niels Henrik Abel}, Springer (2004) 685.
\bibitem{manin13} Yu.~I.~Manin, \emph{Numbers as functions}, arXiv:1312.5160.
\bibitem{Elvang2026} H.~Elvang, A.~Herderschee, R.~Morales, \emph{String theory from maximal supersymmetry}, arXiv:2601.11705.
\bibitem{Veneziano} G.~Veneziano, \emph{Construction of a crossing-symmetric, Regge-behaved amplitude for linearly rising trajectories}, Nuovo Cim.\ A \textbf{57} (1968) 190.
\bibitem{LaportaRemiddi96} S.~Laporta, E.~Remiddi, \emph{The analytical value of the electron $(g-2)$ at order $\alpha^3$ in QED}, Phys.\ Lett.\ B \textbf{379} (1996) 283.
\bibitem{HartnollYang25} S.~A.~Hartnoll, M.~Yang, \emph{The conformal primon gas at the end of time}, JHEP \textbf{07} (2025) 281, arXiv:2502.02661.
\bibitem{DeClerckHartnollYang25} M.~De~Clerck, S.~A.~Hartnoll, M.~Yang, \emph{Wheeler--DeWitt wavefunctions for 5d BKL dynamics, automorphic $L$-functions and complex primon gases}, JHEP \textbf{11} (2025) 160, arXiv:2507.08788.
\bibitem{Julia90} B.~L.~Julia, \emph{Statistical theory of numbers}, in \emph{Number Theory and Physics}, Springer (1990) 276.
\bibitem{Montgomery73} H.~L.~Montgomery, \emph{The pair correlation of zeros of the zeta function}, Proc.\ Symp.\ Pure Math.\ \textbf{24} (1973) 181.
\bibitem{Odlyzko87} A.~M.~Odlyzko, \emph{On the distribution of spacings between zeros of the zeta function}, Math.\ Comp.\ \textbf{48} (1987) 273.
\bibitem{buium05} A.~Buium, \emph{Arithmetic Differential Equations}, Math.\ Surveys Monogr.\ \textbf{118}, AMS (2005).
\bibitem{pacioli1509} L.~Pacioli, \emph{De Divina Proportione}, Venice (1509).
\bibitem{Pletser2018} V.~Pletser, \emph{Fibonacci numbers and the golden ratio in biology, physics, astrophysics, chemistry and technology: a non-exhaustive review}, arXiv:1801.01369.
\bibitem{Jagannathan2021} A.~Jagannathan, \emph{The Fibonacci quasicrystal: case study of hidden dimensions and multifractality}, Rev.\ Mod.\ Phys.\ \textbf{93} (2021) 045001.
\bibitem{Jedrkiewicz2018} O.~Jedrkiewicz et al., \emph{Coherent four-mode parametric generation in a hexagonally poled nonlinear crystal}, Sci.\ Rep.\ \textbf{8} (2018).
\bibitem{Sonnino2024} G.~Sonnino et al., \emph{The golden ratio family of extremal Kerr--Newman black holes and its implications for the cosmological constant}, Axioms \textbf{13} (2024) 720.
\bibitem{Apery} R.~Ap\'ery, \emph{Irrationalit\'e de $\zeta(2)$ et $\zeta(3)$}, Ast\'erisque \textbf{61} (1979) 11.
\bibitem{F1} J.\,A.~Gonz\'alez Garc\'ia \emph{et al.},
  \emph{Odd Zeta Values from Pentagonal $\F_1$-Descent}, companion paper (2026).
  % needs precise citation; DOI in project folder, pending.

\bibitem{Corr} J.\,A.~Gonz\'alez Garc\'ia \emph{et al.},
  \emph{An analogue of Euler's identity for the binary, ternary, and golden bases}, companion paper (2026).
  % needs precise citation; DOI pending (not yet assigned).

\bibitem{HP} J.\,A.~Gonz\'alez Garc\'ia \emph{et al.},
  \emph{Hilbert--P\'olya Primitive Structure of the Complex Plane}, companion paper (2026).
  % needs precise citation; DOI in project folder, pending.

\bibitem{Kiely26} A.~Kiely, D.\,A.~Chisholm, A.~Touil, S.~Deffner, G.~Landi, S.~Campbell,
  Phys.\ Rev.\ A \textbf{113} (2026) 022403.

\bibitem{Jacobson1995} T.~Jacobson,
  \emph{Thermodynamics of spacetime: the Einstein equation of state},
  Phys.\ Rev.\ Lett.\ \textbf{75} (1995) 1260, arXiv:gr-qc/9504004.

\bibitem{Jacobson2016} T.~Jacobson,
  \emph{Entanglement equilibrium and the Einstein equation},
  Phys.\ Rev.\ Lett.\ \textbf{116} (2016) 201101, arXiv:1505.04753.

\bibitem{Verlinde2011} E.~Verlinde,
  \emph{On the origin of gravity and the laws of Newton},
  JHEP \textbf{04} (2011) 029, arXiv:1001.0785.

\bibitem{Verlinde2017} E.~Verlinde,
  \emph{Emergent gravity and the dark universe},
  SciPost Phys.\ \textbf{2} (2017) 016, arXiv:1611.02269.

\bibitem{Landauer61} R.~Landauer, \emph{Irreversibility and heat generation in the computing process}, IBM J.\ Res.\ Dev.\ \textbf{5} (1961) 183.
\bibitem{Bekenstein73} J.\,D.~Bekenstein, \emph{Black holes and entropy}, Phys.\ Rev.\ D \textbf{7} (1973) 2333.
\bibitem{Hawking75} S.\,W.~Hawking, \emph{Particle creation by black holes}, Commun.\ Math.\ Phys.\ \textbf{43} (1975) 199.
\bibitem{GibbonsHawking77} G.\,W.~Gibbons and S.\,W.~Hawking, \emph{Cosmological event horizons, thermodynamics, and particle creation}, Phys.\ Rev.\ D \textbf{15} (1977) 2738.
\bibitem{BrownHenneaux86} J.\,D.~Brown, M.~Henneaux, \emph{Central charges in the canonical realization of asymptotic symmetries: an example from three-dimensional gravity}, Commun.\ Math.\ Phys.\ \textbf{104} (1986) 207.
\bibitem{GKP98} S.\,S.~Gubser, I.\,R.~Klebanov, A.\,M.~Polyakov, \emph{Gauge theory correlators from non-critical string theory}, Phys.\ Lett.\ B \textbf{428} (1998) 105.
\bibitem{Witten98} E.~Witten, \emph{Anti-de Sitter space and holography}, Adv.\ Theor.\ Math.\ Phys.\ \textbf{2} (1998) 253.
\bibitem{RyuTakayanagi06} S.~Ryu, T.~Takayanagi, \emph{Holographic derivation of entanglement entropy from the AdS/CFT correspondence}, Phys.\ Rev.\ Lett.\ \textbf{96} (2006) 181602.
\bibitem{Obied18} G.~Obied, H.~Ooguri, L.~Spodyneiko, C.~Vafa, \emph{De Sitter space and the swampland}, arXiv:1806.08362.
\bibitem{Polchinski98} J.~Polchinski, \emph{String Theory}, Cambridge University Press (1998).

\bibitem{Huerta2019emerge} J.~Huerta, \emph{How space-times emerge from the superpoint}, LMS/EPSRC Durham Symposium on Higher Structures in M-theory (2019), arXiv:1903.02822.
\bibitem{FiorenzaSatiSchreiber15} D.~Fiorenza, H.~Sati, U.~Schreiber, \emph{Super Lie $n$-algebra extensions, higher WZW models and super $p$-branes with tensor multiplet fields}, Int.\ J.\ Geom.\ Methods Mod.\ Phys.\ \textbf{12} (2015) 1550018, arXiv:1308.5264.
\bibitem{lawvere96unity} F.~W.~Lawvere, \emph{Unity and identity of opposites in calculus and physics}, Appl.\ Categ.\ Structures \textbf{4} (1996) 167.
\bibitem{Schreiber13cohesive} U.~Schreiber, \emph{Differential cohomology in a cohesive $\infty$-topos}, arXiv:1310.7930 (2013).
\bibitem{Oberarzbacher2013} F.\,P.~Oberarzbacher, \emph{Los postulados b\'asicos de la filosof\'ia no-dualista del Shaivismo de Cachemira}, Estudios \textbf{104}, vol.~XI, ITAM (2013) 81--91.
\bibitem{Foucault66} M.~Foucault, \emph{The Order of Things: An Archaeology of the Human Sciences} (Les Mots et les Choses), Gallimard (1966); ch.~1 on \emph{Las Meninas}.
\bibitem{Santos2020} G.\,S.~dos Santos, \emph{Arquitetura vitruviana e ret\'orica antiga} [Vitruvian architecture and ancient rhetoric], Archai \textbf{28} (2020) e02804, doi:10.14195/1984-249X\_28\_4.
\bibitem{MaldacenaSusskind13} J.~Maldacena, L.~Susskind, \emph{Cool horizons for entangled black holes}, Fortschr.\ Phys.\ \textbf{61} (2013) 781, arXiv:1306.0533.
\bibitem{AMPS13} A.~Almheiri, D.~Marolf, J.~Polchinski, J.~Sully, \emph{Black holes: complementarity or firewalls?}, JHEP \textbf{02} (2013) 062, arXiv:1207.3123.
\bibitem{Bell64} J.~S.~Bell, \emph{On the Einstein Podolsky Rosen paradox}, Physics \textbf{1} (1964) 195.
\bibitem{Leggett03} A.~J.~Leggett, \emph{Nonlocal hidden-variable theories and quantum mechanics: an incompatibility theorem}, Found.\ Phys.\ \textbf{33} (2003) 1469.
\bibitem{Groblacher07} S.~Gr\"oblacher, T.~Paterek, R.~Kaltenbaek, \v{C}.~Brukner, M.~\.{Z}ukowski, M.~Aspelmeyer, A.~Zeilinger, \emph{An experimental test of non-local realism}, Nature \textbf{446} (2007) 871, arXiv:0704.2529.
\bibitem{FreedmanClauser72} S.~J.~Freedman, J.~F.~Clauser, \emph{Experimental test of local hidden-variable theories}, Phys.\ Rev.\ Lett.\ \textbf{28} (1972) 938.
\bibitem{Aspect82} A.~Aspect, J.~Dalibard, G.~Roger, \emph{Experimental test of Bell's inequalities using time-varying analyzers}, Phys.\ Rev.\ Lett.\ \textbf{49} (1982) 1804.
\bibitem{Weihs98} G.~Weihs, T.~Jennewein, C.~Simon, H.~Weinfurter, A.~Zeilinger, \emph{Violation of Bell's inequality under strict Einstein locality conditions}, Phys.\ Rev.\ Lett.\ \textbf{81} (1998) 5039.
\bibitem{Nobel2022} The Royal Swedish Academy of Sciences, \emph{The Nobel Prize in Physics 2022}: A.~Aspect, J.~F.~Clauser, A.~Zeilinger, for experiments with entangled photons, establishing the violation of Bell inequalities and pioneering quantum information science.
\bibitem{Branciard07} C.~Branciard, A.~Ling, N.~Gisin, C.~Kurtsiefer, A.~Lamas-Linares, V.~Scarani, \emph{Experimental falsification of Leggett's nonlocal variable model}, Phys.\ Rev.\ Lett.\ \textbf{99} (2007) 210407, arXiv:0708.0584.
\end{thebibliography}

